### 2017-02-11 papers.tex
Reorganizes background section

\chapter{Papers}

% =============================================================================
\section{\texttt{IND\_001} - Data Mining Algorithms to Classify Students}

@@

\subsection{Comment}

@@

\subsection{Relevant Points}

@@

\subsection{Work From This Paper}

@@

% =============================================================================
\section{\texttt{IND\_002} - Discovering Decision Knowledge From Web Log
Portfolio For Managing Classroom Processes By Applying Decision Tree And Data
Cube Technology}

@@

% =============================================================================
\section{\texttt{IND\_003} - Predicting Performance From Test Scores Using
Backpropagation and Counterpropagation}

@@

% =============================================================================
\section{\texttt{IND\_004} - Web Usage Mining for Predicting Final Marks of
Students That Use Moodle Courses}

@@

\subsection{Reading Notes}

@@

% =============================================================================
\section{\texttt{IND\_005} - Using Educational Data Mining Methods to Study the
Impact of Virtual Classroom in E-Learning}

@@

% =============================================================================
\section{\texttt{IND\_006} - Predicting students' marks from Moodle logs using
neural network models}

@@

% =============================================================================
\section{\texttt{IND\_007} - Educational data mining: A survey from 1995 to
2005}

@@

% =============================================================================
\section{\texttt{IND\_008} - Educational Data Mining: A Review of the State of
the Art}

>>>>

\section{Initial Papers in Detail}

This section contain long comments about the first papers which were explored
for this project.

% =============================================================================
\subsection{\texttt{IND\_001} - Data Mining Algorithms to Classify Students}

@@

\subsubsection{Comment}

@@

\subsubsection{Relevant Points}

@@

\subsubsection{Work From This Paper}

@@

% =============================================================================
\subsection{\texttt{IND\_002} - Discovering Decision Knowledge From Web Log
Portfolio For Managing Classroom Processes By Applying Decision Tree And Data
Cube Technology}

@@

% =============================================================================
\subsection{\texttt{IND\_003} - Predicting Performance From Test Scores Using
Backpropagation and Counterpropagation}

@@

% =============================================================================
\subsection{\texttt{IND\_004} - Web Usage Mining for Predicting Final Marks of
Students That Use Moodle Courses}

@@

\subsubsection{Reading Notes}

@@

% =============================================================================
\subsection{\texttt{IND\_005} - Using Educational Data Mining Methods to Study the
Impact of Virtual Classroom in E-Learning}

@@

% =============================================================================
\subsection{\texttt{IND\_006} - Predicting students' marks from Moodle logs using
neural network models}

@@

% =============================================================================
\subsection{\texttt{IND\_007} - Educational data mining: A survey from 1995 to
2005}

@@

% =============================================================================
\subsection{\texttt{IND\_008} - Educational Data Mining: A Review of the State of
the Art}
